---
title: "tsneTraining"
author: "Fahimeh"
date: "28/10/2019"
output: word_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(FRESA.CAD)
library(Rtsne)
library(clValid)
library(mclust)
library(EMCluster)
library(dendextend)

```


```{r}
#originaldata <- read_excel("C:/Semesters/Alzheimer's Paper/Dataset/TadClean.xlsx")
originaldata <- read.csv("C:/Semesters/Alzheimer's Paper/Dataset/TADPOLE_D1_D2.csv",na.strings="NA,-4" ) 

load("C:/Semesters/Alzheimer's Paper/Dataset/trainMclust.RDATA")
load("C:/Semesters/Alzheimer's Paper/Dataset/TestMclust.RDATA")


BaselineData <- subset(originaldata, VISCODE == 'bl'& (DX_bl == "LMCI" | DX_bl == "EMCI")) 

baseSubset <- BaselineData[,c("RID","DXCHANGE","DX_bl","PTGENDER","AGE",#"PTEDUCAT",
                          "PTRACCAT","PTMARRY","ICV","PTEDUCAT","APOE4","Entorhinal",
                        "Ventricles","MidTemp","Hippocampus","CDRSB","ADAS11","ADAS13","MMSE",
                          "RAVLT_immediate","RAVLT_learning","RAVLT_forgetting",
                          "RAVLT_perc_forgetting","FAQ")]



data <- na.omit(baseSubset)
Vdata <- na.omit(baseSubset)
rownames(data) <- data$RID

#data$DX_bl[data$DX_bl== "EMCI"] <- 0
#data$DX_bl[data$DX_bl== "LMCI"] <- 1
data$DX_bl <- as.numeric(data$DX_bl)

# data$PTGENDER[data$PTGENDER== "Male"] <- 0
# data$PTGENDER[data$PTGENDER== "Female"] <- 1
data$PTGENDER <- as.numeric(data$PTGENDER)

# data$PTRACCAT[data$PTRACCAT == "Am Indian/Alaskan"] <- 0
# data$PTRACCAT[data$PTRACCAT == "Asian"] <- 1
# data$PTRACCAT[data$PTRACCAT == "Black"] <- 2
# data$PTRACCAT[data$PTRACCAT == "Hawaiian/Other PI"] <- 3
# data$PTRACCAT[data$PTRACCAT == "More than one"] <- 4
# data$PTRACCAT[data$PTRACCAT == "Unknown"] <- 5
# data$PTRACCAT[data$PTRACCAT == "White"] <- 6
data$PTRACCAT <- as.numeric(data$PTRACCAT)

# data$PTMARRY[data$PTMARRY == "Divorced"] <- 0
# data$PTMARRY[data$PTMARRY == "Married"] <- 1
# data$PTMARRY[data$PTMARRY == "Never married"] <- 2
# data$PTMARRY[data$PTMARRY == "Unknown"] <- 3
# data$PTMARRY[data$PTMARRY == "Widowed"] <- 4
data$PTMARRY <- as.numeric(data$PTMARRY)

pdata <- data

dataScaled <- FRESAScale(data[,!(colnames(data) %in% c("RID","DXCHANGE","DX_bl","PTGENDER","PTRACCAT","PTMARRY","PTEDUCAT","APOE4"))],method="Order")$scaledData

# dataScaled <- scale(data[,!(colnames(data) %in% c("DXCHANGE","DX_bl","PTGENDER","PTRACCAT","PTMARRY","PTEDUCAT","APOE4","ConvNLtoMCI","ConvNLtoAD","ConvMCItoAD"))])

##### Select 5 top fearure for nmf cluster ####

dataScaled <- as.data.frame(dataScaled)
Tdata <- cbind(dataScaled,data[,"DX_bl"])
colnames(Tdata)[colnames(Tdata)=="data[, \"DX_bl\"]"] <- "DX_bl"

 topFeat <- univariate_Logit(data=Tdata, Outcome="DX_bl", pvalue=0.05, adjustMethod="BH",uniTest="zIDI",limit=0.008)
 dataRed <- Tdata[,names(topFeat)]
 
dataRed <- dataScaled[,c("Hippocampus","ADAS11","MMSE","RAVLT_immediate","RAVLT_learning" )]
 
minClnm <- apply(dataRed, 2,min)
TnmfData <- dataRed

TnmfData[, "Hippocampus"] <- TnmfData[, "Hippocampus"] + 3
TnmfData[, "ADAS11"] <- TnmfData[, "ADAS11"] + 2
TnmfData[, "RAVLT_immediate"] <- TnmfData[, "RAVLT_immediate"] + 2
TnmfData[, "RAVLT_learning"] <- TnmfData[, "RAVLT_learning"] + 2

############ PCA For Mclust clustering #########

rownames(dataScaled) <- data$RID

dataScaled <- as.data.frame(dataScaled)

pcadata <- prcomp(dataScaled,rank. = 3)$x

###########  NMF DATA  #########
Wdata <- data[,!(colnames(data) %in% c("RID","DXCHANGE","DX_bl","PTGENDER","PTRACCAT","PTMARRY","PTEDUCAT","APOE4"))]

minClnm <- apply(Wdata, 2,min)
nmfData <- Wdata

nmfData[, "RAVLT_learning"] <- nmfData[, "RAVLT_learning"] + 1
nmfData[, "RAVLT_forgetting"] <- nmfData[, "RAVLT_forgetting"] + 4
nmfData[, "RAVLT_perc_forgetting"] <- nmfData[, "RAVLT_perc_forgetting"] + 37


```

```{r}
###################### Mclust ##################

randomSamples <- sample(nrow(dataScaled),0.7*nrow(dataScaled))

traindata <- as.data.frame(dataScaled[randomSamples,])

pcatraindata <- prcomp(traindata,rank. = 3)

pcaTestdata <- predict(pcatraindata,dataScaled[-randomSamples,])


mod1 <- Mclust(pcatraindata$x,G=3)
#save(mod1,file="D:/Fahimeh-SecondSemester/Dataset/trainMclust.RDATA")
load(file="C:/Users/fneja/OneDrive/Documents/EvalCluster/R/Dataset/trainMclust.RDATA")

clusterLabels <- predict(mod1,pcaTestdata)
#save(clusterLabels,file="D:/Fahimeh-SecondSemester/Dataset/TestMclust.RDATA")
load(file="C:/Users/fneja/OneDrive/Documents/EvalCluster/R/Dataset/TestMclust.RDATA")


names(clusterLabels$classification) <- rownames(dataScaled[-randomSamples,])
names(mod1$classification) <- rownames(dataScaled[randomSamples,])


###################### NMF ##################

randomSamples <- sample(nrow(TnmfData),0.7*nrow(TnmfData))

traindata <- as.data.frame(TnmfData[randomSamples,])

testdata <- as.data.frame(TnmfData[-randomSamples,])


nmfcls <- nmfCluster(traindata,rank=3)
#save(nmfcls,file="D:/Fahimeh-SecondSemester/Dataset/trainNMF.RDATA")
load(file="C:/Users/fneja/OneDrive/Documents/EvalCluster/R/Dataset/trainNMF.RDATA")

clusterLabels <- predict(nmfcls,testdata)
#save(clusterLabels,file="D:/Fahimeh-SecondSemester/Dataset/TestNMF.RDATA")
load(file="D:/Fahimeh-SecondSemester/Dataset/TestNMF.RDATA")


names(clusterLabels$classification) <- rownames(TnmfData[-randomSamples,])
names(nmfcls$classification) <- rownames(TnmfData[randomSamples,])

  

cs2 <- clusterStability(data=pcadata, clustermethod=Mclust, randomTests = 100, trainFraction = 0.7,G=2)
save(cs2,file="D:/Fahimeh-SecondSemester/Dataset/cs2.RDATA")
#load(file="D:/Fahimeh-SecondSemester/Dataset/cs2.RDATA")

cs3 <- clusterStability(data=pcadata, clustermethod=Mclust, randomTests = 100, trainFraction = 0.7,G=3)
save(cs3,file="D:/Fahimeh-SecondSemester/Dataset/cs3.RDATA")
#load(file="D:/Fahimeh-SecondSemester/Dataset/cs3.RDATA")

cs4 <- clusterStability(data=pcadata, clustermethod=Mclust, randomTests = 100, trainFraction = 0.7,G=4)
save(cs4,file="D:/Fahimeh-SecondSemester/Dataset/cs4.RDATA")
load(file="D:/Fahimeh-SecondSemester/Dataset/cs4.RDATA")

cs5 <- clusterStability(data=pcadata, clustermethod=Mclust, randomTests = 100, trainFraction = 0.7,G=5)
save(cs5,file="D:/Fahimeh-SecondSemester/Dataset/cs5.RDATA")
#load(file="D:/Fahimeh-SecondSemester/Dataset/cs5.RDATA")

cs6 <- clusterStability(data=pcadata, clustermethod=Mclust, randomTests = 100, trainFraction = 0.7,G=6)
save(cs6,file="D:/Fahimeh-SecondSemester/Dataset/cs6.RDATA")
#load(file="D:/Fahimeh-SecondSemester/Dataset/cs5.RDATA")


############### NMF ##################

# ncs2 <- clusterStability(data=nmfData, clustermethod=nmfCluster, randomTests = 100, trainFraction = 0.7,rank=2)
# save(ncs2,file="D:/Fahimeh-SecondSemester/Dataset/ncs2.RDATA")
# #load(file="D:/Fahimeh-SecondSemester/Dataset/ncs2.RDATA")
# 
# ncs3 <- clusterStability(data=nmfData, clustermethod=nmfCluster, randomTests = 100, trainFraction = 0.7,rank=3)
# save(ncs3,file="D:/Fahimeh-SecondSemester/Dataset/ncs3.RDATA")
# #load(file="D:/Fahimeh-SecondSemester/Dataset/ncs3.RDATA")
# 
# ncs4 <- clusterStability(data=nmfData, clustermethod=nmfCluster, randomTests = 100, trainFraction = 0.7,rank=4)
# save(ncs4,file="D:/Fahimeh-SecondSemester/Dataset/ncs4.RDATA")
# #load(file="D:/Fahimeh-SecondSemester/Dataset/ncs4.RDATA")
# 
# ncs5 <- clusterStability(data=nmfData, clustermethod=nmfCluster, randomTests = 100, trainFraction = 0.7,rank=5)
# save(ncs5,file="D:/Fahimeh-SecondSemester/Dataset/ncs5.RDATA")
# load(file="D:/Fahimeh-SecondSemester/Dataset/ncs5.RDATA")
# 
# ncs6 <- clusterStability(data=nmfData, clustermethod=nmfCluster, randomTests = 100, trainFraction = 0.7,rank=6)
# save(ncs6,file="D:/Fahimeh-SecondSemester/Dataset/ncs6.RDATA")
# load(file="D:/Fahimeh-SecondSemester/Dataset/ncs6.RDATA")
# 
# 
# 
# tncs2 <- clusterStability(data=nmfData, clustermethod=nmfCluster, randomTests = 100, trainFraction = 0.7,rank=2)
# save(tncs2,file="D:/Fahimeh-SecondSemester/Dataset/tncs2.RDATA")
# #load(file="D:/Fahimeh-SecondSemester/Dataset/ncs2.RDATA")
# 
# tncs3 <- clusterStability(data=nmfData, clustermethod=nmfCluster, randomTests = 100, trainFraction = 0.7,rank=3)
# save(tncs3,file="D:/Fahimeh-SecondSemester/Dataset/tncs3.RDATA")
# #load(file="D:/Fahimeh-SecondSemester/Dataset/ncs3.RDATA")
# 
# tncs4 <- clusterStability(data=nmfData, clustermethod=nmfCluster, randomTests = 100, trainFraction = 0.7,rank=4)
# save(tncs4,file="D:/Fahimeh-SecondSemester/Dataset/tncs4.RDATA")
# #load(file="D:/Fahimeh-SecondSemester/Dataset/ncs4.RDATA")
# 
# tncs5 <- clusterStability(data=nmfData, clustermethod=nmfCluster, randomTests = 100, trainFraction = 0.7,rank=5)
# save(tncs5,file="D:/Fahimeh-SecondSemester/Dataset/tncs5.RDATA")
# #load(file="D:/Fahimeh-SecondSemester/Dataset/ncs5.RDATA")
# 
# tncs6 <- clusterStability(data=nmfData, clustermethod=nmfCluster, randomTests = 100, trainFraction = 0.7,rank=6)
# save(tncs6,file="D:/Fahimeh-SecondSemester/Dataset/tncs6.RDATA")
# #load(file="D:/Fahimeh-SecondSemester/Dataset/ncs6.RDATA")


hplot <- gplots::heatmap.2(as.matrix(tncs6$testConsesus),trace="none",main="Test Results: Six Clusters")
cs2$averageNumberofClusters
table(clab <- getConsensusCluster(cs3,who = "testing"))
hplot <- gplots::heatmap.2(as.matrix(tncs6$dataConcensus),trace="none",main="Data Results: Six Clusters")
table(clab <- getConsensusCluster(cs2))
table(clab <- getConsensusCluster(wncs2),data$DX_bl)
hm <- gplots::heatmap.2(as.matrix(cs2$concensusMat),trace="none")
clab <- getConsensusCluster(cs2)
table(clab)
wncs3$pac

############### Training and Testing ####

#clab <- nmfcls$classification
clab <- clusterLabels$classification  ## Test
clab <- mod1$classification  ## Train

#ids <- as.numeric(rownames(data.frame(clab)))
#ids<- data[randomSamples,]$RID 
#ids<- data[-randomSamples,]$RID 

ids <- as.numeric(names(clusterLabels$classification)) # Test
ids <- as.numeric(names(mod1$classification)) # Train

#ids <- data$RID
id <- ids[1]
lastpt <- NULL;
for (id in ids)
{
  stp <- subset(originaldata,RID == id)
  if (nrow(stp) > 1)
  {
    stp <- stp[order(stp$Years_bl),]
    for (i in 2:nrow(stp))
    {
      if (is.na(stp$DXCHANGE[i]) && !is.na(stp$DXCHANGE[i-1]))
      {
        stp$DXCHANGE[i] <- stp$DXCHANGE[i-1];
      }
    }
  }
  lastpt <- rbind(lastpt,stp[which.max(stp$Years_bl),]);
}

rownames(lastpt) <- ids

table(lastpt$DX,lastpt$DX_bl)
table(lastpt$DXCHANGE,lastpt$DX_bl)
lastTPDx <- 1*(lastpt$DXCHANGE == 7 | lastpt$DXCHANGE == 1) + 2*(lastpt$DXCHANGE == 2 | lastpt$DXCHANGE == 4 | lastpt$DXCHANGE == 8) + 3*(lastpt$DXCHANGE == 3 | lastpt$DXCHANGE == 5)
names(lastTPDx) <- rownames(lastpt)

CN_CASES <- subset(lastpt,lastTPDx == 1);
MCI_CASES <- subset(lastpt,lastTPDx == 2);
AD_CASES <- subset(lastpt,lastTPDx == 3);



table(lastTPDx)

ds <- lastpt$RID
#ds <- MCI_CASES$RID
#ds <- AD_CASES$RID
conversionPoint <- NULL;

id <- ds[1]
for (id in ds)
{
  stp <- subset(originaldata,RID == id)
  conversionPoint <- rbind(conversionPoint,stp[stp$DX == "MCI to Dementia" | stp$DX == "Dementia",][1,1:100]);
}

rownames(conversionPoint) <- ds

ADtime <- as.data.frame(cbind(event=rep(1,nrow(conversionPoint)), time = conversionPoint$Years_bl,class=clab[as.character(ds)],data[as.character(ds),!(colnames(data) %in% c("RID","DXCHANGE","PTRACCAT","PTMARRY","ConvNLtoMCI","ConvNLtoAD","ConvMCItoAD"))]))


# extract the number NC , MCI and AD of each cluster

CNclass <- clab[as.character(CN_CASES$RID)]
MCIclass <- clab[as.character(MCI_CASES$RID)]
ADclass <- clab[as.character(AD_CASES$RID)]

CN <- numeric()
MCI <- numeric()
AD <- numeric()

for(i in 1:length(unique(clab)))
{
  CN <- cbind(CN , length(CNclass[CNclass == i]))
  MCI <- cbind(MCI , length(MCIclass[MCIclass == i]))
  AD <- cbind(AD , length(ADclass[ADclass == i]))
}


## Create labels for visualization

lastTPDx<- as.character(lastTPDx)

lastTPDx[lastTPDx == 1] <- "CN"
lastTPDx[lastTPDx == 2] <- "MCI"
lastTPDx[lastTPDx == 3] <- "AD"


### Plotting with survival package

library(ggfortify)
library(survival)
ADtime <- as.data.frame(ADtime)

fit <- survfit(Surv(time, event ) ~ class , data = ADtime)
autoplot(fit)

tiff("test.tiff", units="in", width=5, height=5, res=600)
# insert ggplot code
autoplot(fit)
dev.off()

autoplot(fit, surv.linetype = 'dashed', conf.int = FALSE,
         censor.shape = '*', censor.size = 5, facets = TRUE, ncol = 2)


#diffAD_curve <- subset(ADtime, (class == 1 | class == 2))
diffAD_curve <- subset(ADtime, ( class == 2)) #class == 3 |
diffAD_curve <- as.data.frame(diffAD_curve)

survdiff(Surv(time, event ) ~ class , data = diffAD_curve)


############# visualization ##########

           ############# t-SNE #########

Labels<-clusterLabels$classification
clusterLabels$classification <-as.factor(clusterLabels$classification)

## for plotting
colors = rainbow(length(unique(clusterLabels$classification)))
names(colors) = unique(clusterLabels$classification)

## Executing the algorithm on curated data

Visualdata <- dataScaled[c(names(clusterLabels$classification)),]

#tsne <- Rtsne(unique(TnmfData[-randomSamples,]), dims = 2, perplexity=30, verbose=TRUE, max_iter = 500)

tsne <- Rtsne(unique(Visualdata), dims = 2, perplexity=40, verbose=TRUE, max_iter = 5000)

## Plotting
plot(as.data.frame(tsne$Y), t='p', main="t-sne NMF (Test) (K=3)",col=colors[as.numeric(as.factor(lastTPDx))])

plot(tsne$Y, t='n',xlab = "tsneX",ylab = "tsneY", main="t-sne Mclust (Test)",col="darkgreen")
text(as.data.frame(tsne$Y), labels=lastTPDx, col=colors[clusterLabels$classification])


 ###### PCA ######

Visualdata <- pcadata[c(names(clusterLabels$classification)),]

plot(Visualdata[,1:2],xlab="PC1", ylab="PC2",col = clusterLabels$classification ,main="PCA Mclust (Test)");
text(as.data.frame(Visualdata), labels=lastTPDx, col=colors[clusterLabels$classification])


#Standard Error -----> MSE

library(psych)


describe(ADtime[ADtime$class == 1,]$time)
describe(ADtime[ADtime$class == 2,]$time)
describe(ADtime[ADtime$class == 3,]$time)


#describe(data[ds,]$Hippocampus)
describe(ADtime[ADtime$class == 1,]$Hippocampus)
describe(ADtime[ADtime$class == 2,]$Hippocampus)
describe(ADtime[ADtime$class == 3,]$Hippocampus)

#describe(data[ds,]$Entorhinal)
describe(ADtime[ADtime$class == 1,]$Entorhinal)
describe(ADtime[ADtime$class == 2,]$Entorhinal)
describe(ADtime[ADtime$class == 3,]$Entorhinal)


#describe(data[ds,]$ICV)
describe(ADtime[ADtime$class == 1,]$ICV)
describe(ADtime[ADtime$class == 2,]$ICV)
describe(ADtime[ADtime$class == 3,]$ICV)


#describe(data[ds,]$Ventricles)
describe(ADtime[ADtime$class == 1,]$Ventricles)
describe(ADtime[ADtime$class == 2,]$Ventricles)
describe(ADtime[ADtime$class == 3,]$Ventricles)

#describe(data[ds,]$MidTemp)
describe(ADtime[ADtime$class == 1,]$MidTemp)
describe(ADtime[ADtime$class == 2,]$MidTemp)
describe(ADtime[ADtime$class == 3,]$MidTemp)


#describe(data[ds,]$CDRSB)
describe(ADtime[ADtime$class == 1,]$CDRSB)
describe(ADtime[ADtime$class == 2,]$CDRSB)
describe(ADtime[ADtime$class == 3,]$CDRSB)


#describe(data[ds,]$MMSE)
describe(ADtime[ADtime$class == 1,]$MMSE)
describe(ADtime[ADtime$class == 2,]$MMSE)
describe(ADtime[ADtime$class == 3,]$MMSE)


#describe(data[ds,]$ADAS13)
describe(ADtime[ADtime$class == 1,]$ADAS13)
describe(ADtime[ADtime$class == 2,]$ADAS13)
describe(ADtime[ADtime$class == 3,]$ADAS13)


#describe(data[ds,]$ADAS11)
describe(ADtime[ADtime$class == 1,]$ADAS11)
describe(ADtime[ADtime$class == 2,]$ADAS11)
describe(ADtime[ADtime$class == 3,]$ADAS11)


#describe(data[ds,]$RAVLT_immediate)
describe(ADtime[ADtime$class == 1,]$RAVLT_immediate)
describe(ADtime[ADtime$class == 2,]$RAVLT_immediate)
describe(ADtime[ADtime$class == 3,]$RAVLT_immediate)


#describe(data[ds,]$RAVLT_learning)
describe(ADtime[ADtime$class == 1,]$RAVLT_learning)
describe(ADtime[ADtime$class == 2,]$RAVLT_learning)
describe(ADtime[ADtime$class == 3,]$RAVLT_learning)


#describe(data[ds,]$FAQ)
describe(ADtime[ADtime$class == 1,]$FAQ)
describe(ADtime[ADtime$class == 2,]$FAQ)
describe(ADtime[ADtime$class == 3,]$FAQ)

#describe(data[ds,]$RAVLT_perc_forgetting)
describe(ADtime[ADtime$class == 1,]$RAVLT_perc_forgetting)
describe(ADtime[ADtime$class == 2,]$RAVLT_perc_forgetting)
describe(ADtime[ADtime$class == 3,]$RAVLT_perc_forgetting)


#describe(data[ds,]$RAVLT_forgetting)
describe(ADtime[ADtime$class == 1,]$RAVLT_forgetting)
describe(ADtime[ADtime$class == 2,]$RAVLT_forgetting)
describe(ADtime[ADtime$class == 3,]$RAVLT_forgetting)


#describe(data[ds,]$AGE_BL)
describe(ADtime[ADtime$class == 1,]$AGE)
describe(ADtime[ADtime$class == 2,]$AGE)
describe(ADtime[ADtime$class == 3,]$AGE)

#describe(data[ds,]$PTEDUCAT)
describe(ADtime[ADtime$class == 1,]$PTEDUCAT)
describe(ADtime[ADtime$class == 2,]$PTEDUCAT)
describe(ADtime[ADtime$class == 3,]$PTEDUCAT)


#describe(data[ds,]$APOE4)
# describe(ADtime[ADtime$class == 1,]$APOE4)
# describe(ADtime[ADtime$class == 2,]$APOE4)
# describe(ADtime[ADtime$class == 3,]$APOE4)

apoe40<- numeric()
apoe41<- numeric()
apoe42<- numeric()

for(i in 1:3)
{
  z0 <- ADtime[ADtime$class == i,]$APOE4 == 0
  apoe40 <- cbind(apoe40 , length(z0[z0 == TRUE]))
  
  z1 <- ADtime[ADtime$class == i,]$APOE4 == 1
  apoe41 <- cbind(apoe41 , length(z1[z1 == TRUE]))
  
  z2 <- ADtime[ADtime$class == i,]$APOE4 == 2
  apoe42 <- cbind(apoe42 , length(z2[z2 == TRUE]))
}



male <- numeric()
female <- numeric()

for(i in 1:3)
{
  MA <- ADtime[ADtime$class == i,]$PTGENDER == 1
  male <- cbind(male , length(MA[MA == TRUE]))
  
  FE <- ADtime[ADtime$class == i,]$PTGENDER == 2
  female <- cbind(female , length(FE[FE == TRUE]))
}


LMCI <- numeric()
EMCI <- numeric()

for(i in 1:3)
{
  L <- ADtime[ADtime$class == i,]$DX_bl == 4
  LMCI <- cbind(LMCI , length(L[L == TRUE]))
  
  E <- ADtime[ADtime$class == i,]$DX_bl == 3
  EMCI <- cbind(EMCI , length(E[E == TRUE]))
}

###### ANOVA Test #######

class <- as.numeric(ADtime$class)

aov_cont<- aov(class ~ ADtime$time)
summary(aov_cont)[[1]][["Pr(>F)"]][[1]]

aov_cont<- aov(class ~ ADtime$Hippocampus)
summary(aov_cont)[[1]][["Pr(>F)"]][[1]]

aov_cont<- aov(class ~ ADtime$Entorhinal)
summary(aov_cont)[[1]][["Pr(>F)"]][[1]]

aov_cont<- aov(class ~ ADtime$ICV)
summary(aov_cont)[[1]][["Pr(>F)"]][[1]]

aov_cont<- aov(class ~ ADtime$Ventricles)
summary(aov_cont)[[1]][["Pr(>F)"]][[1]]

aov_cont<- aov(class ~ ADtime$MidTemp)
summary(aov_cont)[[1]][["Pr(>F)"]][[1]]

aov_cont<- aov(class ~ ADtime$CDRSB)
summary(aov_cont)[[1]][["Pr(>F)"]][[1]]

aov_cont<- aov(class ~ ADtime$MMSE)
summary(aov_cont)[[1]][["Pr(>F)"]][[1]]

aov_cont<- aov(class ~ ADtime$ADAS13)
summary(aov_cont)[[1]][["Pr(>F)"]][[1]]

aov_cont<- aov(class ~ ADtime$ADAS11)
summary(aov_cont)[[1]][["Pr(>F)"]][[1]]

aov_cont<- aov(class ~ ADtime$RAVLT_immediate)
summary(aov_cont)[[1]][["Pr(>F)"]][[1]]

aov_cont<- aov(class ~ ADtime$RAVLT_learning)
summary(aov_cont)[[1]][["Pr(>F)"]][[1]]

aov_cont<- aov(class ~ ADtime$FAQ)
summary(aov_cont)[[1]][["Pr(>F)"]][[1]]    

aov_cont<- aov(class ~ ADtime$RAVLT_perc_forgetting)
summary(aov_cont)[[1]][["Pr(>F)"]][[1]]

aov_cont<- aov(class ~ ADtime$RAVLT_forgetting)
summary(aov_cont)[[1]][["Pr(>F)"]][[1]]

aov_cont<- aov(class ~ ADtime$AGE)
summary(aov_cont)[[1]][["Pr(>F)"]][[1]]  

aov_cont<- aov(class ~ ADtime$PTEDUCAT)
summary(aov_cont)[[1]][["Pr(>F)"]][[1]]


############# chi-square test #########

Achs_apoe4 <- chisq.test(ADclass ,ADtime$APOE4)
Achs_gender <- chisq.test(ADclass ,ADtime$PTGENDER)


Mchs_apoe4 <- chisq.test(MCIclass ,ADtime$APOE4)
Mchs_gender <- chisq.test(MCIclass ,ADtime$PTGENDER)


########### CHARACTERISTIC ###########

data <- ADtime

Fe <- length(data$PTGENDER[data$PTGENDER==1])
Ma <- length(data$PTGENDER[data$PTGENDER==2])

LMCI <- length(data$DX_bl[data$DX_bl==4])
EMCI <- length(data$DX_bl[data$DX_bl==3])

EMCI_F <- subset(data, DX_bl == 3 &  PTGENDER == 1) 
EMCI_M <- subset(data, DX_bl == 3 &  PTGENDER == 2) 

LMCI_F <- subset(data, DX_bl == 4 &  PTGENDER == 1) 
LMCI_M <- subset(data, DX_bl == 4 &  PTGENDER == 2) 

##### AGE #####
Age_EMCI <- data$AGE[data$DX_bl==3]
mean.result <- mean(Age_EMCI)
sd.result = sqrt(var(Age_EMCI)) 

Age_LMCI <- data$AGE[data$DX_bl==4]
mean.result <- mean(Age_LMCI)
sd.result = sqrt(var(Age_LMCI)) 

##### MMSE #####
MMSE_EMCI <- data$MMSE[data$DX_bl==3]
mean.result <- mean(MMSE_EMCI)
sd.result = sqrt(var(MMSE_EMCI)) 

MMSE_LMCI <- data$MMSE[data$DX_bl==4]
mean.result <- mean(MMSE_LMCI)
sd.result = sqrt(var(MMSE_LMCI)) 

##### ADAS13 #####
ADAS13_EMCI <- data$ADAS13[data$DX_bl==3]
mean.result <- mean(ADAS13_EMCI)
sd.result = sqrt(var(ADAS13_EMCI)) 

ADAS13_LMCI <- data$ADAS13[data$DX_bl==4]
mean.result <- mean(ADAS13_LMCI)
sd.result = sqrt(var(ADAS13_LMCI)) 

##### ADAS11 #####
ADAS11_EMCI <- data$ADAS11[data$DX_bl==3]
mean.result <- mean(ADAS11_EMCI)
sd.result = sqrt(var(ADAS11_EMCI)) 

ADAS11_LMCI <- data$ADAS11[data$DX_bl==4]
mean.result <- mean(ADAS11_LMCI)
sd.result = sqrt(var(ADAS11_LMCI)) 

##### CDRSB #####
CDRSB_EMCI <- data$CDRSB[data$DX_bl==3]
mean.result <- mean(CDRSB_EMCI)
sd.result = sqrt(var(CDRSB_EMCI)) 

CDRSB_LMCI <- data$CDRSB[data$DX_bl==4]
mean.result <- mean(CDRSB_LMCI)
sd.result = sqrt(var(CDRSB_LMCI)) 

##### RAVLT_immediate #####
RAVLT_immediate_EMCI <- data$RAVLT_immediate[data$DX_bl==3]
mean.result <- mean(RAVLT_immediate_EMCI)
sd.result = sqrt(var(RAVLT_immediate_EMCI)) 

RAVLT_immediate_LMCI <- data$RAVLT_immediate[data$DX_bl==4]
mean.result <- mean(RAVLT_immediate_LMCI)
sd.result = sqrt(var(RAVLT_immediate_LMCI)) 

##### RAVLT_learning #####
RAVLT_learning_EMCI <- data$RAVLT_learning[data$DX_bl==3]
mean.result <- mean(RAVLT_learning_EMCI)
sd.result = sqrt(var(RAVLT_learning_EMCI)) 

RAVLT_learning_LMCI <- data$RAVLT_learning[data$DX_bl==4]
mean.result <- mean(RAVLT_learning_LMCI)
sd.result = sqrt(var(RAVLT_learning_LMCI)) 

##### RAVLT_perc_forgetting #####
RAVLT_perc_forgetting_EMCI <- data$RAVLT_perc_forgetting[data$DX_bl==3]
mean.result <- mean(RAVLT_perc_forgetting_EMCI)
sd.result = sqrt(var(RAVLT_perc_forgetting_EMCI)) 

RAVLT_perc_forgetting_LMCI <- data$RAVLT_perc_forgetting[data$DX_bl==4]
mean.result <- mean(RAVLT_perc_forgetting_LMCI)
sd.result = sqrt(var(RAVLT_perc_forgetting_LMCI)) 

##### RAVLT_forgetting #####
RAVLT_forgetting_EMCI <- data$RAVLT_forgetting[data$DX_bl==3]
mean.result <- mean(RAVLT_forgetting_EMCI)
sd.result = sqrt(var(RAVLT_forgetting_EMCI)) 

RAVLT_forgetting_LMCI <- data$RAVLT_forgetting[data$DX_bl==4]
mean.result <- mean(RAVLT_forgetting_LMCI)
sd.result = sqrt(var(RAVLT_forgetting_LMCI)) 

##### FAQ #####
FAQ_EMCI <- data$FAQ[data$DX_bl==3]
mean.result <- mean(FAQ_EMCI)
sd.result = sqrt(var(FAQ_EMCI) 

FAQ_LMCI <- data$FAQ[data$DX_bl==4]
mean.result <- mean(FAQ_LMCI)
sd.result = sqrt(var(FAQ_LMCI)) 

##### Entorhinal #####
Entorhinal_EMCI <- data$Entorhinal[data$DX_bl==3]
mean.result <- mean(Entorhinal_EMCI)
sd.result = sqrt(var(Entorhinal_EMCI) 

Entorhinal_LMCI <- data$Entorhinal[data$DX_bl==4]
mean.result <- mean(Entorhinal_LMCI)
sd.result = sqrt(var(Entorhinal_LMCI)) 


##### Hippocampus #####
Hippocampus_EMCI <- data$Hippocampus[data$DX_bl==3]
mean.result <- mean(Hippocampus_EMCI)
sd.result = sqrt(var(Hippocampus_EMCI) 

Hippocampus_LMCI <- data$Hippocampus[data$DX_bl==4]
mean.result <- mean(Hippocampus_LMCI)
sd.result = sqrt(var(Hippocampus_LMCI)) 


##### MidTemp #####
MidTemp_EMCI <- data$MidTemp[data$DX_bl==3]
mean.result <- mean(MidTemp_EMCI)
sd.result = sqrt(var(MidTemp_EMCI))

MidTemp_LMCI <- data$MidTemp[data$DX_bl==4]
mean.result <- mean(MidTemp_LMCI)
sd.result = sqrt(var(MidTemp_LMCI)) 


##### Ventricles #####
Ventricles_EMCI <- data$Ventricles[data$DX_bl==3]
mean.result <- mean(Ventricles_EMCI)
sd.result = sqrt(var(Ventricles_EMCI))

Ventricles_LMCI <- data$Ventricles[data$DX_bl==4]
mean.result <- mean(Ventricles_LMCI)
sd.result = sqrt(var(Ventricles_LMCI)) 


##### ICV #####
ICV_EMCI <- data$ICV[data$DX_bl==3]
mean.result <- mean(ICV_EMCI)
sd.result = sqrt(var(ICV_EMCI))

ICV_LMCI <- data$ICV[data$DX_bl==4]
mean.result <- mean(ICV_LMCI)
sd.result = sqrt(var(ICV_LMCI)) 



##### Education #####
Education_EMCI <- data$PTEDUCAT[data$DX_bl==3]
mean.result <- mean(Education_EMCI)
sd.result = sqrt(var(Education_EMCI))

Education_LMCI <- data$PTEDUCAT[data$DX_bl==4]
mean.result <- mean(Education_LMCI)
sd.result = sqrt(var(Education_LMCI)) 


APOE1 <- data$APOE4[data$DX_bl==3 & data$APOE4==1]
APOE2 <- data$APOE4[data$DX_bl==3 & data$APOE4==2]
APOE0 <- data$APOE4[data$DX_bl==3 & data$APOE4==0]

APOE1 <- data$APOE4[data$DX_bl==4 & data$APOE4==1]
APOE2 <- data$APOE4[data$DX_bl==4 & data$APOE4==2]
APOE0 <- data$APOE4[data$DX_bl==4 & data$APOE4==0]


stats::t.test(ADtime$PTGENDER,ADtime1$PTGENDER)
stats::t.test(ADtime[ADtime$class == 1,]$AGE,ADtime1[ADtime1$class == 1,]$AGE)
stats::t.test(ADtime[ADtime$class == 2,]$AGE,ADtime1[ADtime1$class == 2,]$AGE)
stats::t.test(ADtime[ADtime$class == 3,]$AGE,ADtime1[ADtime1$class == 3,]$AGE)

stats::t.test(ADtime[ADtime$class == 1,]$time,ADtime1[ADtime1$class == 1,]$time)
stats::t.test(ADtime[ADtime$class == 2,]$time,ADtime1[ADtime1$class == 2,]$time)
stats::t.test(ADtime[ADtime$class == 3,]$time,ADtime1[ADtime1$class == 3,]$time)

stats::t.test(ADtime[ADtime$class == 1,]$PTEDUCAT,ADtime1[ADtime1$class == 1,]$PTEDUCAT)
stats::t.test(ADtime[ADtime$class == 2,]$PTEDUCAT,ADtime1[ADtime1$class == 2,]$PTEDUCAT)
stats::t.test(ADtime[ADtime$class == 3,]$PTEDUCAT,ADtime1[ADtime1$class == 3,]$PTEDUCAT)

stats::t.test(ADtime[ADtime$class == 3,]$MMSE,ADtime1[ADtime1$class == 3,]$MMSE)
stats::t.test(ADtime[ADtime$class == 1,]$MMSE,ADtime1[ADtime1$class == 1,]$MMSE)
stats::t.test(ADtime[ADtime$class == 2,]$MMSE,ADtime1[ADtime1$class == 2,]$MMSE)
stats::t.test(ADtime$MMSE,ADtime1$MMSE)


# class <- as.numeric(ADtime$class)
# class1 <- as.numeric(ADtime1$class)
# 
# aov_cont<- aov(class ~ ADtime$time, class1 ~ ADtime1$time)
# summary(aov_cont)[[1]][["Pr(>F)"]][[1]]

###########MCI to AD conversion ODDS ratio ####
data <- subset(ADtime,class== 1)

Ma <- length(data$PTGENDER[data$PTGENDER==2])

data <- subset(ADtime,class== 1)

APOE1 <- subset(data,APOE4==1)
APOE2 <- subset(data,APOE4==2)
APOE0 <- subset(data,APOE4==0)

data <- subset(ADtime,class== 1)

mean.result <- mean(data$time)
sd.result = var(data$time)
mean.result
sd.result

data <- subset(ADtime,class== 3)

mean.result <- mean(data$AGE)
sd.result = var(data$AGE)
mean.result
sd.result

data <- subset(ADtime,class== 1)

mean.result <- mean(data$ICV)
sd.result = var(data$ICV)
mean.result
sd.result

data <- subset(ADtime,class== 3)

mean.result <- mean(data$PTEDUCAT)
sd.result = var(data$PTEDUCAT)
mean.result
sd.result

data <- subset(ADtime,class== 1)

mean.result <- mean(data$Entorhinal)
sd.result = var(data$Entorhinal)
mean.result
sd.result

data <- subset(ADtime,class== 3)

mean.result <- mean(data$Ventricles)
sd.result = var(data$Ventricles)
mean.result
sd.result

data <- subset(ADtime,class== 1)

mean.result <- mean(data$MidTemp)
sd.result = var(data$MidTemp)
mean.result
sd.result

data <- subset(ADtime,class== 1)

mean.result <- mean(data$Hippocampus)
sd.result = var(data$Hippocampus)
mean.result
sd.result

data <- subset(ADtime,class== 3)

mean.result <- mean(data$CDRSB)
sd.result = var(data$CDRSB)
mean.result
sd.result

data <- subset(ADtime,class== 1)

mean.result <- mean(data$ADAS11)
sd.result = var(data$ADAS11)
mean.result
sd.result

data <- subset(ADtime,class== 3)

mean.result <- mean(data$ADAS13)
sd.result = var(data$ADAS13)
mean.result
sd.result

data <- subset(ADtime,class== 1)

mean.result <- mean(data$MMSE)
sd.result = var(data$MMSE)
mean.result
sd.result

data <- subset(ADtime,class== 3)

mean.result <- mean(data$RAVLT_immediate)
sd.result = var(data$RAVLT_immediate)
mean.result
sd.result

data <- subset(ADtime,class== 1)

mean.result <- mean(data$RAVLT_learning)
sd.result = var(data$RAVLT_learning)
mean.result
sd.result

data <- subset(ADtime,class== 3)

mean.result <- mean(data$RAVLT_forgetting)
sd.result = var(data$RAVLT_forgetting)
mean.result
sd.result

data <- subset(ADtime,class== 1)

mean.result <- mean(data$RAVLT_perc_forgetting)
sd.result = var(data$RAVLT_perc_forgetting)
mean.result
sd.result

data <- subset(ADtime,class== 3)

mean.result <- mean(data$FAQ)
sd.result = var(data$FAQ)
mean.result
sd.result

